
\section{Product Backlog}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}


\begin{longtable}{|L{0.8cm}|L{3.5cm}|L{1.2cm}|L{1.2cm}|L{4cm}|L{3cm}|}
\hline
\rowcolor{gray!30}
\multicolumn{6}{|c|}{\textbf{PRODUCT BACKLOG}} \\
\hline
\rowcolor{gray!20}
\textbf{ID} & \textbf{Name} & \textbf{Imp} & \textbf{Est} & \textbf{How to demo} & \textbf{Notes} \\
\hline
\endfirsthead
\hline
\rowcolor{gray!30}
\multicolumn{6}{|c|}{\textbf{PRODUCT BACKLOG (continued)}} \\
\hline
\rowcolor{gray!20}
\textbf{ID} & \textbf{Name} & \textbf{Imp} & \textbf{Est} & \textbf{How to demo} & \textbf{Notes} \\
\hline
\endhead
\hline
\endfoot
1 & User registration & 10 & 7 & Create account with username and password, and show it in \textit{''database-file''} on disk & Check input format is correct \\
\hline
2 & User login & 10 & 5 & Enter username and password, Show access to logged in frontpage & Check input format is correct \\
\hline
3 & Search and stream content & 9 & 10 & Log in as user, search for content and show search results & Show message if there are no results  \\
\hline
4 & Manage playlist & 8 & 7 & Log in as user, choose a playlist and reorder tracks. Rename playlist. & Tracks are added to playlist from search results page (not in here)  \\
\hline
5 & Receive recommendations & 7 & 5 & Log in as user, listen to tracks, show that frontpage updates with new tracks based on this  & Show a default list of songs if no history found \\
\hline
6 & Manage subscriptions & 8 & 4 & Log in as user, click ''upgrade'', enter payment information, shows a ''Premium user" badge. & Payment must succeed, user allowed to abort/downgrade\\
\hline
7 & Upload and manage catalog & 9 & 7 & Log in as artist, upload and publish song. Show it in search results.  & Only mp3 (or wav?) allowed, otherwise error message\\
\hline
8 & Manage users & 6 & 5 & Log in as administrator, choose "edit" and modify user information. Choose "delete" and delete a user. Confirm changes & Users are added using ''registration''. Maybe allow to add custom users during development \\
\hline
9 & Manage content & 6 & 5 & Log in as administrator, edit and delete content items  & Show updated content \\
\hline
10 & Configure tier settings & 5 & 4 & Set audio quality levels for free and premium tiers. Verify by streaming in free and premium account &  Maybe use wav for premium, and mp3 for free \\

\hline
\end{longtable}